\documentclass[12pt]{examdesign}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{amsfonts}
\usepackage{pgfplots}
\usepackage{pifont}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage[american]{circuitikz}

\SectionFont{\large\sffamily}
\Fullpages
\ContinuousNumbering
\usepackage{ulem}
\ProportionalBlanks{2}


\DefineAnswerWrapper{}{}
\NumberOfVersions{1}
%\IncludeFromFile{foobar.tex}
\examname{\Large{Acceleration}}
\class {\Large Physics}

\def \namedata {Name: \hrulefill\\ 
	Date: \hrulefill \\
	Period: \hrulefill \\
	Primary Peer Reviewer: \hrulefill 
	\\
			\begin{tabular}{| p{1cm} | p{1cm} | p{1 cm} | p{1cm} |}
	\hline
		+1 & 0 & -1 & $\Sigma$ 
		\\
		\hline
		& & & \vspace{.5cm}
		\\ \hline
	
	\end{tabular}
	\\
 \vspace{-.6in}
	
}




\begin{document}




\begin{multiplechoice} [title={Multiple Choice},
	rearrange=no]
	\textit{Choose the best answer to each question.} 
	
	\begin{question}
	What is the best description of acceleration?
	 \choice {How fast an object is traveling.}
	 \choice {How far an object travels in a certain amount of time.}
	 \choice {How much an object slides or spins.}
	 \choice [!]{Speeding up, slowing down, or changing direction.}
	\end{question}



	\begin{question}
	NASA's Aries 1 Rocket can go from 0 m/s to 445 m/s in 57 seconds.  What is its acceleration?
	\choice {0.016 m/s\textsuperscript{2}}
	\choice [!]{7.807 m/s\textsuperscript{2}}
	\choice {25365 m/s\textsuperscript{2}}
	\choice {There is not enough information to solve this problem.}
\end{question}

	\begin{question}
	A man rolls a ball up a hill with an initial speed of 2 m/s. 10 seconds later, it is traveling at 5.2 m/s down the hill.  What is the ball's acceleration?
	\choice [!]{-0.72 m/s\textsuperscript{2}}
	\choice {0.32 m/s\textsuperscript{2}}
	\choice {52 m/s\textsuperscript{2}}
	\choice {10791.859 m/s\textsuperscript{2}}
\end{question}


\end{multiplechoice}

\begin{multiplechoice} [title={Multiple Correct Multiple Choice},
	rearrange=no]
	\textit{For the following question, \textbf{choose two} correct answers.  No credit will be given for incorrect or partially correct answers.  Mark \textbf{both} answers clearly.} 


	\begin{question}
		Which of the following objects are \textbf{NOT} accelerating?
	\choice [!]{A car that is stopped at a red light.}
	\choice {An airplane that is turning.}
	\choice {A racecar as it begins a race.}
	\choice [!]{A boat traveling at a constant speed, in a straight line, on a calm lake.}
	\choice {A coin that is dropped and falls to the ground.}
\end{question}

\end{multiplechoice}


\begin{shortanswer}[title={Free Response},
	rearrange=no]


\begin{question}
A penny is dropped from the top of a 30-meter tall building.  It hits the ground 2.473 seconds later.  
	\begin{enumerate}
		\item What is the average speed of the penny? 
		\vspace{1in}
	\item What is the final velocity of the penny?
	\vspace{1in}
	\item What is the acceleration of the penny?
		\vspace{1in}
\end{enumerate}
\end{question}

\begin{question}
Your 12-year old little brother hears you mention that an object is ``accelerating at 4 meters per second per second," and wants to know what this means.  In a clear, coherent paragraph of at least 5 sentences, explain to him what it means for an object to ``accelerate at 4 meters per second per second."


	\end{question}

	\end{shortanswer}



\end{document}


