\documentclass[10pt]{examdesign}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{amsfonts}
\usepackage{pgfplots}
\usepackage{pifont}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage{gensymb}
\usepackage[american]{circuitikz}

\SectionFont{\large\sffamily}
\Fullpages
\ContinuousNumbering
\usepackage{ulem}
\ProportionalBlanks{2}


\DefineAnswerWrapper{}{}
\NumberOfVersions{1}
%\IncludeFromFile{foobar.tex}
\examname{\Large{Friction}}
\class {\Large Physics}

\def \namedata {Name: \hrulefill\\ 
	Date: \hrulefill \\
	Period: \hrulefill \\
	Primary Peer Reviewer: \hrulefill 
	\\
			\begin{tabular}{| p{1cm} | p{1cm} | p{1 cm} | p{1cm} |}
	\hline
		+1 & 0 & -1 & $\Sigma$ 
		\\
		\hline
		& & & \vspace{.5cm}
		\\ \hline
	
	\end{tabular}
	\\
 \vspace{-.6in}
	
}




\begin{document}




\begin{multiplechoice} [title={Multiple Choice},
	rearrange=no]


	
	\begin{question}
What are the two factors that affect the friction force between two surfaces?
\choice{mass and weight}
\choice[!]{type of surface and how hard the surfaces push together}
\choice{mass and distance}
\choice{type of surface and amount of gravity}
	\end{question}



\begin{question}
What is one way you could reduce the friction between two surfaces?
\choice[!]{put oil on the surfaces}
\choice{put glue on the surfaces}
\choice{allow one surface to rust}
\choice{make one of the surfaces rougher.}
\end{question}

\begin{question}
What kind of friction occurs when objects are not moving?
\choice{Static friction}
\choice{Fluid friction}
\choice{Sliding friction}
\choice{Rolling friction}
\end{question}

\begin{question}
Gymnasts often use chalk on their hands.  This is to - 
\choice{decrease friction}
\choice{increase friction}
\choice{increase gravity}
\choice{decrease gravity}
\end{question}

\begin{question}
	Friction always acts - 
	\choice{opposite any motion}
	\choice{opposite the tendency to move}
	\choice{Both A and B}
	\choice{none of the above}
\end{question}


\begin{question}
Which of the following would be the most slippery surface?
\choice{Teflon $\mu = 0.04 $}
\choice{Ice $\mu = 0.05 $}
\choice{Bananna Peel $\mu = 0.066 $}
\choice{Rubber $\mu = 1.02 $}
	\end{question}



\begin{question}
Your are thinking about cooking an egg for breakfast.  Which pan should you choose to use the least amount of oil, yet still not have the egg stick?
\choice{Well seasoned cast iron - $\mu = 0.15$ }
\choice{Teflon - $\mu = 0.04 $ }
\choice{Aluminum - $\mu = 0.3 $}
\choice{Ceramic (like Copper Chef, etc.) $\mu = 0.17 $}

	\end{question}

\end{multiplechoice} 

\begin{shortanswer} [title={Free Response},
	rearrange=no]
	
	\begin{question}
		List 2 situations in which friction is \textbf{bad}.  Explain why it is bad in each situation.
		
		\begin{enumerate}
			\item
			
		
			 
			\item 	 \vspace{1 in}
	
		\end{enumerate}
		\end{question}
	
	
		\begin{question}
		 \vspace{1 in}	List 2 situations in which friction is \textbf{good}.  Explain why it is bad in each situation.
		
		\begin{enumerate}
			\item

			\item 
			\vspace{1 in}
		\end{enumerate}
	\end{question}
	

	
	\end{shortanswer}



\end{document}


