\documentclass[12pt]{examdesign}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{amsfonts}
\usepackage{pgfplots}
\usepackage{pifont}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage[american]{circuitikz}

\SectionFont{\large\sffamily}
\Fullpages
\ContinuousNumbering
\usepackage{ulem}
\ProportionalBlanks{2}


\DefineAnswerWrapper{}{}
\NumberOfVersions{1}
%\IncludeFromFile{foobar.tex}
\examname{\Large{3 Weeks' Exam}}
\class {\large AP Physics 1}

\def \namedata {Name: \hrulefill\\ 
	Date: \hrulefill \\
	Period: \hrulefill \\
	Primary Peer Reviewer: \hrulefill 
	\\
			\begin{tabular}{| p{1cm} | p{1cm} | p{1 cm} | p{1cm} |}
	\hline
		+1 & 0 & -1 & $\Sigma$ 
		\\
		\hline
		& & & \vspace{.5cm}
		\\ \hline
	
	\end{tabular}
	\\
 \vspace{-.8in}
	
}




\begin{document}




\begin{multiplechoice} [title={Multiple Choice},
	rearrange=no]
	\textit{Choose the best answer to each question.} 
	
	\begin{question}
	What is $ (4 \times 10^3) (2 \times 10^{30})$
	 \choice [!]{$8 \times 10^{33}$}
	 \choice {$72 \times 10^{90}$}
	 \choice {$6 \times 10^{27} $ }
	 \choice {$2 \times 10^{-27}$}
	\end{question}

	\begin{question}
	Alan walks 3 miles to the north, then turns and walks 4 miles to the east.  What are his distance and displacement at the end of the journey?  
	\choice {$d = 3$ miles north and $\vec{d} = 4$ miles east}
	\choice [!]{$d = 7$ miles and $\vec{d} = 5$ miles northeast}
	\choice {$d = 5$ miles and $\vec{d} = 7$ miles northeast}
	\choice {$d = 7$ miles and $\vec{d} = 7$ miles northeast}
\end{question}

	\begin{question}
	Raul runs 400 meters at 8 m/s, then he walks 400 meters at 4 m/s. What is his average speed?
	\choice [!]{5.333 m/s}
	\choice {6 m/s}
	\choice {7.154 m/s}
	\choice {8 m/s}
\end{question}

\begin{question}
	Sarah and Jackie are playing tag.  Sarah is chasing Jackie at a speed of 6 m/s.  Jackie is running away at a speed of 4 m/s.  If they start 15m apart, how long will it be until Sarah tags Jackie?
	\choice {0.667 s}
	\choice {1.5 s}
	\choice [!]{7.5 s}
	\choice {30 s}

	\end{question}

\begin{question}
Solve $k = \frac{1}{2} m v^2$ for v. 
	\choice {$v = \sqrt{\frac{2k}{m}} $}
	\choice {$v = (\frac{2k}{m})^2$}
	\choice {$v=\sqrt{\frac{k}{2m}}$}
	\choice {None of the above}
	
\end{question}


\end{multiplechoice}

\begin{multiplechoice} [title={Multiple Correct Multiple Choice},
	rearrange=no]
	\textit{For the following question, \textbf{choose two} correct answers.  No credit will be given for incorrect or partially correct answers.  Mark \textbf{both} answers clearly.} 


	\begin{question}
		Which of the following are measured in m/s?
	\choice {Distance}
	\choice [!]{Velocity}
	\choice [!]{Speed}
	\choice {Displacement}
	\choice{Temperature}
\end{question}

\end{multiplechoice}


\begin{shortanswer}[title={Free Response},
	rearrange=no]
\begin{question}
Christy drives at 37 m/s for 25 seconds.  How far did she drive?
\vspace{1in} 

\end{question}

\begin{question}
Billy-Bob is driving his truck at 30 m/s to the east when he sees a goat running toward him from the other direction at 7 m/s.  He first sees the goat when it is 200 m away.
\begin{enumerate}
	\item How long does Billy-Bob have to swerve out of the way?

\vspace{1in}
\item What is the distance the goat will run during that time?


\end{enumerate}
	
\end{question}



	\end{shortanswer}



\end{document}


