\documentclass[12pt]{examdesign}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{amsfonts}
\usepackage{pgfplots}
\usepackage{pifont}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage[american]{circuitikz}

\SectionFont{\large\sffamily}
\Fullpages
\ContinuousNumbering
\usepackage{ulem}
\ProportionalBlanks{2}


\DefineAnswerWrapper{}{}
\NumberOfVersions{1}
%\IncludeFromFile{foobar.tex}
\examname{\Large{Distance, Velocity and Time}}
\class {\Large Physics}

\def \namedata {Name: \hrulefill\\ 
	Date: \hrulefill \\
	Period: \hrulefill \\
	Primary Peer Reviewer: \hrulefill 
	\\
			\begin{tabular}{| p{1cm} | p{1cm} | p{1 cm} | p{1cm} |}
	\hline
		+1 & 0 & -1 & $\Sigma$ 
		\\
		\hline
		& & & \vspace{.5cm}
		\\ \hline
	
	\end{tabular}
	\\
 \vspace{-.6in}
	
}




\begin{document}




\begin{multiplechoice} [title={Multiple Choice},
	rearrange=no]
	\textit{Choose the best answer to each question.} 


	\begin{question}
	A car is traveling at 60 mph (26.823 m/s).  At this speed, how long would it take for the car to travel a quarter mile (402.336 m)?
	\choice {0.067 s}
	\choice [!]{15 s}
	\choice {240 s}
	\choice {10791.859 s}
\end{question}

	\begin{question}
	A toy travels at a speed of 0.325 m/s for 17 seconds.  How far does the toy travel?
	\choice {0.019 m}
	\choice [!]{5.525 m}
	\choice {17 m}
	\choice {52.308 m}
\end{question}

\begin{question}
Which of the following is a vector that tells you how far it is from where an object began moving to where it ended up, regardless of its path?
	\choice {$\vec{d}$}
	\choice {$d$}
	\choice {$\vec{v}$}
	\choice {$v$}

	\end{question}




\end{multiplechoice}

\begin{multiplechoice} [title={Multiple Correct Multiple Choice},
	rearrange=no]
	\textit{For the following question, \textbf{choose two} correct answers.  No credit will be given for incorrect or partially correct answers.  Mark \textbf{both} answers clearly.} 


	\begin{question}
		Which of the following are vectors? (CHOOSE TWO)
	\choice {Distance}
	\choice [!]{Velocity}
	\choice {Speed}
	\choice [!] {Displacement}
	\choice{Temperature}
\end{question}



\begin{question}
	A woman runs completely around a 400-meter track in 60 seconds.  What are the woman's average speed and average velocity?   (CHOOSE TWO)
	\choice {$v=0$ m/s}
	\choice {$v=6.667$ m/s}
	\choice {$\vec{v}=0$ m/s}
	\choice {$\vec{v} = 6.667$ m/s to the south}
	\choice{The woman's average velocity cannot be determined without more information. }
\end{question}

\end{multiplechoice}


\begin{shortanswer}[title={Free Response},
	rearrange=no]


\begin{question}
A swallow travels at 11 m/s.  If it flies for 3 minutes, how far will it travel?
Be sure to include the following:
\begin{itemize}
	\item Diagram with labels.
	\item Formula without changes.
	\item Manipulated formula.
	\item Substitution
	\item Final Answer with units.
	\item Annotations.
\end{itemize}

\end{question}



	\end{shortanswer}



\end{document}


