\documentclass[10pt]{examdesign}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{amsfonts}
\usepackage{pgfplots}
\usepackage{pifont}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage[american]{circuitikz}

\SectionFont{\large\sffamily}
\Fullpages
\ContinuousNumbering
\usepackage{ulem}
\ProportionalBlanks{2}


\DefineAnswerWrapper{}{}
\NumberOfVersions{1}
%\IncludeFromFile{foobar.tex}
\examname{\Large{Quiz: Fluids}}
\class{ {\Large AP Physics 2}}

\def \namedata {Name: \hrulefill\\ 
	Date: \hrulefill \\
	Period: \hrulefill \\
	Peer Reviewer: \hrulefill \\
	Authentication Code: \hrulefill
	\\
		
	\begin{tabular}{| p{1cm} | p{1cm} | p{1 cm} | p{1cm} |}
	\hline
		+1 & 0 & -1 & $\Sigma$ 
		\\
		\hline
		& & & \vspace{.5cm}
		\\ \hline
	
	\end{tabular}
	\\
 \vspace{-.6in}
	
}




\begin{document}




\begin{truefalse}[title={True or False},
	rearrange=no]
	\begin{question}
		\answer{False} Objects that float in water must be lighter than they water they are floating in. 
	\end{question}

	\begin{question}
		\answer{True} The density of an object and the density of the fluid determine whether an object will float or sink.
	\end{question}

	\begin{question}
	\answer{False} Wood always floats and metal always sinks.
\end{question}
	 
	\begin{question}
		\answer{True} Heating air causes its molecules to move faster.
	\end{question}
	\begin{question}
	\answer{False} Liquid rises up a straw because of suction.
\end{question}

\begin{question}
	\answer{True} Hydrostatic pressure does not depend on the shape of the fluid's container, only the depth below the surface. 
\end{question}

\begin{question}
	\answer{False} Fluids that are moving exert a higher pressure on their surroundings.
\end{question}

\begin{question}
	\answer{True} A cylindrical pipe of diameter 2-cm is connected to another cylindrical pipe of diameter 1-cm.  When water flows through the pipe, it flows faster in the 1-cm section. 
	
\end{question}


\begin{question}
	\answer{False} Water always flows downward, toward the lowest point.
\end{question}

\begin{question}
	\answer{True}  Using a U-shaped glass tube, it is possible to create a bridge-like structure that connects two fishtanks and allows fish to swim from one tank to the other.  
\end{question}

\begin{question}
	\answer{False}  "Fluid" and "liquid" mean the same thing.
\end{question}

\begin{question}
	\answer{True} A graduated cylinder is placed on a scale and half-filled with water.  A metal object is supported with a thin wire, and carefully lowered into the cylinder so that it is completely immersed in the water, but does not touch the bottom or sides of the graduated cylinder.  The reading on the scale increases. 
\end{question}

\begin{question}
	\answer{False}  Opening the windows during a tornado is a good idea, as it will equalize the pressure between the inside and outside of the house and minimize damage.
\end{question}


\begin{question}
	\answer{True}  Water is forced through a dam due to hydrostatic pressure.
\end{question}

\begin{question}
	\answer{False}  Few creatures live in the very deepest parts of the ocean because the pressure is so great, it would kill them. 
\end{question}

\begin{question}
	\answer{True}  Bernouli's Equation is really just a statement of the Law of Conservation of Energy. 
\end{question}



\end{truefalse}




\end{document}


