\documentclass[10pt]{examdesign}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{amsfonts}
\usepackage{pgfplots}
\usepackage{pifont}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage[american]{circuitikz}

\SectionFont{\large\sffamily}
\Fullpages
\ContinuousNumbering
\usepackage{ulem}
\ProportionalBlanks{2}


\DefineAnswerWrapper{}{}
\NumberOfVersions{1}
%\IncludeFromFile{foobar.tex}
\examname{\Large{Quiz: Magnetism}}
\class{ {\Large AP Physics 2}}

\def \namedata {Name: \hrulefill\\ 
	Date: \hrulefill \\
	Period: \hrulefill \\
	Peer Reviewer: \hrulefill \\
	Authentication Code: \hrulefill
	\\
		
	\begin{tabular}{| p{1cm} | p{1cm} | p{1 cm} | p{1cm} |}
	\hline
		+1 & 0 & -1 & $\Sigma$ 
		\\
		\hline
		& & & \vspace{.5cm}
		\\ \hline
	
	\end{tabular}
	\\
 \vspace{-.6in}
	
}




\begin{document}




\begin{truefalse}[title={True or False},
	rearrange=no]
	
	\begin{question}
		\answer{False} All metals are attracted to a magnet.
	\end{question}

	\begin{question}
		\answer{True} Magnetic fields are created by moving charges.
	\end{question}

	\begin{question}
	\answer{False} All permanent magnets are made of iron.
\end{question}
	 
	\begin{question}
		\answer{True} Charged particles that are moving in a magnetic field can move along a circular, helical, or linear path, depending on their orientation to the magnetic field. 
	\end{question}
	\begin{question}
	\answer{False} Larger magnets are always stronger than smaller magnets.
\end{question}

\begin{question}
	\answer{True} If a permanent magnet is heated enough, it will eventually lose its magnetism. 
\end{question}

\begin{question}
	\answer{False} The magnetic and geographic poles of the earth are located at the same place.
\end{question}

\begin{question}
	\answer{True} A magnetic field is infinite in size. 
	
\end{question}


\begin{question}
	\answer{False} Only permanent magnets produce magnetic fields.
\end{question}

\begin{question}
	\answer{True}  A changing magnetic field will cause current to flow in a nearby loop of wire.
\end{question}

\begin{question}
	\answer{False}  Magnetic fields can be canceled by electrostatic fields. 
\end{question}

\begin{question}
	\answer{True} Magnetic forces can be canceled by electrostatic forces.
\end{question}

\begin{question}
	\answer{False}  The Earth's north magnetic pole is located near the Earth's geographic north pole.
\end{question}


\begin{question}
	\answer{True} Two parallel wires that carry current in the same direction will be attracted to each other.
\end{question}

\begin{question}
	\answer{False}  Magnets repel non-metals.
\end{question}

\begin{question}
	\answer{True}  Like poles repel and unlike poles attract.
\end{question}




    
    \begin{question}
    	\answer{True}  The magnitude of a cross product can be calculated by multiplying the magnitude of the two vectors and then multiplying by the sin of the angle between them. 
    	
    \end{question}
    
   
\begin{question}
	\answer{True}  If the earth had no magnetic field, there would be no auroras.
\end{question}


\begin{question}
	\answer{False}  If the earth had no magnetic field, humans would not be able to generate electricity.
\end{question}

\begin{question}
	\answer{False}  A electron is at rest in a magnetic field directed to the right.  It will accelerate to the left. 
\end{question}

\begin{question}
	\answer{True} A dot product is a way to multiply two vectors and get a scalar. \pagebreak
	\end{question}


\end{truefalse}

\begin{multiplechoice}[title={Multiple Choice},
	rearrange=no]
\begin{question}
	A magnetic field is directed into the page, but it is not known how or whether the magnetic field is changing.  A counterclockwise current is induced in a loop of wire that is oriented in the plane of the page.  How is the magnetic field changing?
	\choice{The magnetic field is getting stronger.}
	\choice{The magnetic field is getting weaker.}
	\choice{The magnetic field is remaining constant.}
	\choice{There is not enough information to determine how the field is changing.}
\end{question}



	\begin{question}
		Two long, parallel wires are oriented horizontally.  Both wires carry the same amount of current in the +x direction.  What is the magnetic force that the wires exert on each other?
		\choice{The magnetic force is attractive.}
		\choice{The magnetic force is repulsive.}
		\choice{The magnetic force causes the wires to rotate.}
		\choice{There is no magnetic force in this situation.}
	\end{question}

	\begin{question}
	An electron travels toward the top of the page through a magnetic field that is directed out of the page.  The magnetic force on the electron is directed - 
	\choice{to the left.}
	\choice{to the right.}
	\choice{toward the top of the page.}
	\choice{toward the bottom of the page.}
	\choice{into the page.}
 	\choice{out of the page.}
\end{question}




\begin{question}
On September 1, 1859, an extremely powerful solar flare struck the earth, known as the Carrington Event.  This event disrupted the Earth's magnetic field enough to cause powerful Aurora all over the planet.  Many telegraph operators were shocked, and reported papers on their desks catching fire.  Which of the following equations would be most useful in determining why the telegraphs malfunctioned?
		\choice{$\varepsilon = - \frac{\Delta \Phi_B}{\Delta t}$}
		\choice{$\vec{F}_B = q \vec{v} \times \vec{B}$}
		\choice{$\vec{F}_B = I \vec{\ell} \times \vec{B}$}
		\choice{$B = \frac{\mu_0}{2\pi}\frac{I}{r}$}
	\end{question}






\begin{question}
	
A 2-Tesla magnetic field is directed to the left.  A particle has a charge of 0.03 C, and is moving to the right as a speed of 4 m/s.  What is the force that is felt by the particle?
\choice{.64 N}
\choice{0.36 N}
\choice{0.24 N}
\choice{0 N}


\end{question}
	

	
	



	\end{multiplechoice}




\end{document}


