\documentclass[11pt]{examdesign}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{amsfonts}
\usepackage{pgfplots}
\usepackage{pifont}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage[american]{circuitikz}

\SectionFont{\large\sffamily}
\Fullpages
\ContinuousNumbering
\usepackage{ulem}
\ProportionalBlanks{2}


\DefineAnswerWrapper{}{}
\NumberOfVersions{1}
%\IncludeFromFile{foobar.tex}
\examname{\Large{Pre-Solo Written Test}}
\class {\Large Flight Training}

\def \namedata {Name: \hrulefill\\ 
	Date: \hrulefill \\
    CFI: \hrulefill 


	
}




\begin{document}




\begin{multiplechoice} [title={Multiple Choice},
	rearrange=no]
	\vspace{0.1in}

\begin{question}
	What is the purpose of the Federal Aviation Regulations (FARs)?
	\choice {To regulate air traffic control operations}
	\choice {To govern the use of airspace}
	\choice [!]{To establish rules and regulations for pilot and aircraft operations}
	\choice {To set standards for aircraft maintenance and repair}
\end{question}

\begin{question}
	What is the relationship between lift and weight during cruise flight?
	\choice {Lift is greater than weight, causing the aircraft to climb}
	\choice {Weight is greater than lift, causing the aircraft to descend}
	\choice [!]{Lift and weight are equal, causing the aircraft to maintain altitude}
	\choice {Lift has no effect on weight in flight}
\end{question}

\begin{question}
	What is the purpose of an aircraft's fuel system?
	\choice {To generate electricity to power the aircraft's systems}
	\choice {To provide hydraulic pressure to operate the aircraft's flight controls}
	\choice [!]{To store and supply fuel to the engine for combustion}
	\choice {To regulate the temperature inside the aircraft cabin}
\end{question}

\begin{question}
	What is a weather front?
	\choice [!]{A boundary between two different types of air masses}
	\choice {A line that connects points of equal atmospheric pressure}
	\choice {A rotating column of air extending from a thunderstorm to the ground}
	\choice {A cloud formation that resembles a horizontal cylinder}
\end{question}

\begin{question}
	What is a VOR?
	\choice {A device used for measuring airspeed}
	\choice {A navigation aid that provides information on the aircraft's altitude}
	\choice {A system used for communicating with air traffic control}
	\choice [!]{A navigation aid that provides information on the aircraft's direction}
\end{question}

\begin{question}
	What is the meaning of the acronym "ELT" in aviation?
	\choice {Emergency Landing Technique}
	\choice {Electronic Light Transmission}
	\choice [!]{Emergency Locator Transmitter}
	\choice {Electronic Load Test}
\end{question}

\begin{question}
	What is the function of the ailerons?
	\choice{To control pitch}
	\choice{To control yaw}
	\choice[!]{To control roll}
	\choice{To control engine power}
\end{question}

\begin{question}
	What is the purpose of the flight control surface known as the elevator?
	\choice{To control roll}
	\choice{To control yaw}
	\choice[!]{To control pitch}
	\choice{To control engine power}
\end{question}

\begin{question}
	What is the difference between true airspeed and indicated airspeed?
	\choice{True airspeed is measured without errors, indicated airspeed includes errors}
	\choice[!]{Indicated airspeed is measured by the airspeed indicator, true airspeed is corrected for altitude and temperature}
	\choice{True airspeed is measured in kilometers per hour, indicated airspeed is measured in knots}
	\choice{Indicated airspeed is the maximum airspeed of the aircraft, true airspeed is the cruising airspeed}
\end{question}

\begin{question}
	What is the purpose of the pitot-static system?
	\choice{To control the fuel mixture in the engine}
	\choice[!]{To measure airspeed and altitude}
	\choice{To maintain proper tire pressure}
	\choice{To reduce drag on the airplane}
\end{question}






\end{multiplechoice}




\end{document}


