\chapter{Gas Laws}
Unlike liquids, gasses are easily compressible.  Thus, the compressibility of the gasses must be taken into account when discussing how the gasses behave in relation to temperature and pressure.   There are four terms that must be defined with relation to gasses:
\begin{itemize}
	\item An \textbf{\textit{adiabatic}} \index{Adiabatic} process is one in which no heat flows.  Adiabatic processes take place in either a perfectly insulated environment or happen quickly enough that the amount of heat that flows into or out of the surrounding environment is negligible. 
	
	\item An \textit{\textbf{isothermal}} \index{Isothermal} process is one in which the temperature remains constant throughout the process.  This is done by adding or removing heat from the system.  
	
	\item In an \textbf{\textit{isobaric}} \index{isobaric} process, the pressure of the sample remains constant.  
	
	\item Finally, in an \textit{\textbf{isochoric}} \index{isochoric} process, the volume of the gas does not change.  This is sometimes called isovolumetric. 
	\end{itemize}
	
Before we begin our study of gas laws, it is important to note that all temperatures must be on an absolute scale.  This text will use the Kelvin scale.   To convert from celsius to kelvin, simply add 273.15: 
	
		\begin{mdframed}[backgroundcolor=orange!20!white]
		\begin{equation}
			T_K = T_C + 273.15\si{K}
			\label{equation:celsiuskelvinconvertion}
		\end{equation}
	\end{mdframed}	


	\section{Boyle's, Charles's, Gay-Lussac's, and The Combined Gas Law}
	You may remember from chemistry that the temperature (T), pressure (P), and volume (V) of a gas are all related.  In fact, an isothermal process will be governed by \textit{Boyle's Law}: \index{Boyle's Law}
	
	\begin{mdframed}[backgroundcolor=orange!20!white]
		\begin{equation}
			P_1 V_1 = P_2 V_2
			\label{equation:boyleslaw}
		\end{equation}
	\end{mdframed}	

Similarly, an isobaric process is governed by \textit{Charles's Law}: \index{Charles's Law}
	\begin{mdframed}[backgroundcolor=orange!20!white]
	\begin{equation}
		\frac{V_1}{T_1} = \frac{V_2}{T_2}
		\label{equation:charleslaw}
	\end{equation}
\end{mdframed}	

And the \textit{Gay-Lussac Law} describes isochoric processes: \index{Gay-Lussac Law}
\begin{mdframed}[backgroundcolor=orange!20!white]
	\begin{equation}
		\frac{P_1}{T_1} = \frac{P_2}{T_2}
		\label{equation:gaylussaclaw}
	\end{equation}
\end{mdframed}	

After the discovery of these three laws, scientists used these to create the \textbf{\textit{Combined Gas Law}}: \index{Combined Gas Law} \index{Gas Law, Combined}
\begin{mdframed}[backgroundcolor=orange!20!white]
	\begin{equation}
		\frac{P_1V_1}{T_1} = \frac{P_2V_2}{T_2}
		\label{equation:combinedgaslaw}
	\end{equation}
\end{mdframed}

Rather than trying to remember each relationship, it is often easier to always apply the combined gas law to a situation.  Whatever variable is held constant will appear on both sides of the equation, and thus be eliminated.  



\begin{mdframed}[backgroundcolor=blue!10!white]
	\begin{center}
		
		
		\textbf{Example \thesection.1}	
	\end{center}
	
	\textbf{Problem: }A balloon has a volume of $0.1 \si{m^3}$ at room temperature ($20\si{\degreeCelsius}$).  What would its volume be if placed into a blast chiller at $-40\si{\degreeCelsius}$?  
	
	
	\vspace{0.1in}
	
	\textbf{Solution:} Begin by converting all temperatures to kelvin. By Equation \ref{equation:celsiuskelvinconvertion},
	\begin{equation*}
		T_1 = T_{C1} + 273.15\si{K} = 20 \si{\degreeCelsius} + 273.15\si{K} = 293.15 \si{K}
	\end{equation*}
		\begin{equation*}
		T_2 = T_{C2} + 273.15\si{K} = -40 \si{\degreeCelsius} + 273.15\si{K} = 233.15 \si{K}
	\end{equation*}

	Since there is no mention of changing pressure, we can assume that both states occur at atmospheric pressure, and thus the process is isobaric.  Using the combined gas law:
	\begin{equation*}
		\frac{\cancel{P_1}V_1}{T_1} = \frac{\cancel{P_2}V_2}{T_2}
	\end{equation*}	

		Solving for $V_2$ yields:
		
	\begin{equation*}
	V_2= \frac{V_1 T_2}{T_1} = \frac{0.1 \si{m^3} \times 233.15 \si{K}}{293.15 \si{K}} \approx \boxed{7.953 \times 10^{-2} \si{m^3}}
\end{equation*}	
\end{mdframed}

	
	\section{The Ideal Gas Law} \index{Ideal Gas Law} \index {Gas Law, Ideal}
	The ideal gas law states:
	
	\begin{mdframed}[backgroundcolor=orange!20!white]
		\begin{equation}
			PV = nRT
			\label{equation:universalgaslawr}
		\end{equation}
	\end{mdframed}
where P is pressure, V is volume, T is temperature, n is the number of moles of gas that make up the sample and R is the universal gas constant:
\index{Universal Gas Constant}
\index{Gas Constant}

	\begin{mdframed}[backgroundcolor=green!20!white]
	\begin{equation*}
		R = \SI{8.31446261815324}{\frac{J}{mol\cdot K}}
		\label{constant:universalgas}
	\end{equation*}
\end{mdframed}	


Sometimes, it is useful to know the exact number of molecules in a sample without having to convert from moles.  The following formula allows one to determine N, the number of molecules in a sample.
	
		\begin{mdframed}[backgroundcolor=orange!20!white]
		\begin{equation}
			PV = N k_BT
			\label{equation:universalgaslawkb}
		\end{equation}
	\end{mdframed}

In this equation, $k_B$ is known as \textbf{Boltzmann's Constant} \index{Boltzmann's Constant} , which is the Universal Gas Constant divided by Avagadro's Number:


	\begin{mdframed}[backgroundcolor=green!20!white]
	\begin{equation*}
		k_B = 1.380649 \times 10^{-23}\si{\frac{J}{K}}
		\label{constant:boltzman}
	\end{equation*}
\end{mdframed}		
	
\begin{mdframed}[backgroundcolor=blue!10!white]
	\begin{center}
		
		
		\textbf{Example \thesection.1}	
	\end{center}
	
	\textbf{Problem: } A sample of gas occupies $0.5 \si{m^3}$ at a pressure of $101325 \si{Pa}$ and a temperature of $300 \si{K}$.  Find
	\begin{enumerate}[label=(\alph*)]
		\item the number of moles the sample contains.
		\item the number of molecules the sample contains.
	\end{enumerate}
	
	
	\vspace{0.1in}
	
	\textbf{Solution:} 

	
	\begin{enumerate}[label=(\alph*)]
	
		\item begin by using Equation \ref{equation:universalgaslawr}:
		\begin{equation*}
			PV = nRT
		\end{equation*}
		
		Solving for n and substituting gives: 
		
		\begin{equation*}
			n= \frac{PV}{RT} = \frac{(101325 \si{Pa})(0.5 \si{m^3})}{(\SI{8.314}{\frac{J}{mol\cdot K}})(300 \si{K})} \approx \boxed{\SI{20.312}{mol}}
		\end{equation*}
		
		\item to solve for the number of molecules, use Equation \ref{equation:universalgaslawkb}:
		\begin{equation*}
			PV = N k_BT
		\end{equation*}
		
		Solving for N and substituting gives: 
		
			\begin{equation*}
			n= \frac{PV}{k_BT} = \frac{(101325 \si{Pa})(0.5 \si{m^3})}{(	k_B = 1.381 \times 10^{-23}\si{\frac{J}{K}})(300 \si{K})} \approx \boxed{1.228 \times 10^{25} \si{molecules}}
		\end{equation*}
		
	\end{enumerate}

\end{mdframed}	
	
		
	\section{Internal Energy of a Gas}
			\subsection{Absolute Internal Energy}
			\index{Internal Energy}
				The internal energy of an ideal gas can be thought of as the total of the kinetic energies of all molecules in the sample.  The internal energy of the gas is given by:
				
	\begin{mdframed}[backgroundcolor=orange!20!white]
		\begin{equation}
			U = \frac{3}{2}nRT = \frac{3}{2} N k_BT
			\label{equation:internalenergy}
		\end{equation}
	\end{mdframed}

	\subsection{Change in Internal Energy} \index{Internal Energy, Change in}
	
	Removing all the internal energy from a sample of gas would require the sample to reach a temperature of absolute zero, which is prohibited by the 3rd law of thermodynamics.  Therefore, it is often more important to think about the change in internal energy of the sample.  The internal energy of a gas will change when either heat ($Q$) or work ($W$) flow into or out of the system: 
	
		\begin{mdframed}[backgroundcolor=orange!20!white]
		\begin{equation}
			\Delta U = Q + W
			\label{equation:changeinternalenergy}
		\end{equation}
	\end{mdframed}
	
	There are several sign conventions associated with Equation \ref{equation:changeinternalenergy} that are sometimes confusing to students.  The easiest way to remember is that energy that flows \textit{into} a system causes its internal energy to \textit{increase}, and energy that flows \textit{out} of a system causes its energy to decrease.  Positive and negative signs should be assigned to work and heat that cause this to be true, despite any sign conventions of an equation.  Remember to \textit{understand} the process that is occurring, and do not just blindly follow an equation. 
	
	\newpage
	
	\section{PV-Diagrams} \index{PV Diagram}
	\index{Pressure-Volume Diagram}
	A \textbf{PV-Diagram} will show the relationship of pressure and volume for a sample of gas, with pressure on the y-axis and volume on the x-axis.  

\begin{figure}[h]
		\caption{A PV Diagram for a Sample of Gas} \label{figure:pv1}
	\centering
	\begin{tikzpicture}
		
		\draw[thin,gray!40] (0,0) grid (5,5);
		\draw[<->] (0,0)--(5,0) node[right]{$V (\si{m^3})$};
		\draw[<->] (0,0)--(0,5) node[above]{$P (\si{kPa})$};
		\draw[line width=2pt,blue,-stealth](4,1) -- (2.5,1) node[below]{A} -- (1,1) ;
		\draw[line width=2pt,blue,-stealth](1,1)-- (1,2.5) node [left] {B} -- (1,4);
		\draw[line width=2pt,blue,-stealth] plot[blue,variable=\t,samples=1000,domain=-33:0] ({16*sec(\t)-15},{4.6*(tan(\t))+4});
		\draw [blue](2.5,2.5) node[right] {C};
		\draw (0,1) node[left] {1};
		\draw (0,2) node[left] {2};
		\draw (0,3) node[left] {3};
		\draw (0,4) node[left] {4};
		\draw (0,5) node[left] {5};
		
		\draw (1,0) node[below] {1};
		\draw (2,0) node[below] {2};
		\draw (3,0) node[below] {3};
		\draw (4,0) node[below] {4};
		\draw (5,0) node[below] {5};		
		
	\end{tikzpicture}

\end{figure}
	
Different processes will have different characteristic shapes on the PV Diagram.  In figure \ref{figure:pv1}, the process labeled A is isobaric, because the pressure does not change.  Process B is Isochoric, since the volume is constant.  Process C would likely be either adiabatic or isothermal, since pressure and volume follow a hyperbolic curve.


The area under any process on a PV diagram is equal to the amount of work that flows either into or out of the gas.  In general, in processes pointing toward the left, work is done \textit{on} the gas (and thus the internal energy increases), whereas in processes pointing toward the right, work is done \textit{by} the gas (causing the internal energy to decrease). One should note that there is no area under a vertical line.  Thus, in isochoric processes - such as process B in figure \ref{figure:pv1}, in which the volume does not change, there is no work done. 

\begin{mdframed}[backgroundcolor=blue!10!white]
	\begin{center}
		
		
		\textbf{Example \thesection.1}	
	\end{center}
	
	\textbf{Problem: } A sample of Gas is taken through the process ABC, as shown in the PV diagram below: 
	

\begin{center}
		\begin{tikzpicture}
			
			\draw[thin,gray!40] (0,0) grid (5,5);
			\draw[<->] (0,0)--(5,0) node[right]{$V (\si{m^3})$};
			\draw[<->] (0,0)--(0,5) node[above]{$P (\si{kPa})$};
			\draw[line width=2pt,blue,-stealth](4,1) -- (2.5,1) node[below]{A} -- (1,1) ;
			\draw[line width=2pt,blue,-stealth](1,1)-- (1,2.5) node [left] {B} -- (1,4);
			\draw[line width=2pt,blue,-stealth] plot[blue,variable=\t,samples=1000,domain=-33:0] ({16*sec(\t)-15},{4.6*(tan(\t))+4});
			\draw [blue](2.5,2.5) node[right] {C};
			\draw (0,1) node[left] {1};
			\draw (0,2) node[left] {2};
			\draw (0,3) node[left] {3};
			\draw (0,4) node[left] {4};
			\draw (0,5) node[left] {5};
			
			\draw (1,0) node[below] {1};
			\draw (2,0) node[below] {2};
			\draw (3,0) node[below] {3};
			\draw (4,0) node[below] {4};
			\draw (5,0) node[below] {5};		
			
		\end{tikzpicture}
\end{center}		
		
	The temperature of the gas at the starting point is 300K.  Calculate:
		\begin{enumerate}[label=(\alph*)]
			\item The temperature of the gas at the end of Process A.
			\item The number of molecules in the sample.
			\item The amount of work done in process A.
			\item the amount of work done in process B.
		\end{enumerate}
		
	\vspace{0.1in}
	
	\textbf{Solution:} 
	\begin{enumerate}[label=(\alph*)]
		\item Use the combined gas law, Equation \ref{equation:combinedgaslaw} to find the temperature at the end of process A:
		
		\begin{equation*}
			\frac{P_1V_1}{T_1}=\frac{P_2V_2}{T_2}
		\end{equation*}
	Since the pressure does not change, this equation reduces to Charles's Law:
		\begin{equation*}
		\frac{\cancel{P_1}V_1}{T_1}=\frac{\cancel{P_2}V_2}{T_2} \rightarrow \frac{V_1}{T_1}=\frac{V_2}{T_2}
	\end{equation*}

	Solving for $T_2$ gives:
	\begin{equation*}
		T_2 = \frac{V_2T_1}{V_1} =\frac{(1 \si{m^3}) (300 \si{K})}{4 \si{m^3}} = \boxed{75 \si{K}}
	\end{equation*}

	\item The Ideal Gas Law, Equation \ref{equation:universalgaslawkb}, can be applied to the gas at any point on the diagram.  Here, it is applied in the initial state:
	
	\begin{equation*}
		PV=Nk_BT
	\end{equation*}
	Solving for N gives:
		\begin{equation*}
		N=\frac{PV}{k_BT} = \frac{(1 \times 10^3 \si{Pa})(4 \si{m^3})}{(1.381 \times 10^{-23} \si{J/K})(300 \si{K})} \approx \boxed{9.655 \times 10^{23} \si{molecules}}
	\end{equation*}
		
		\item The work done by process A is equal to the area under the line for process A: 
		
		\begin{center}
			\begin{tikzpicture}
				
				\draw[thin,gray!40] (0,0) grid (5,5);
				\draw[<->] (0,0)--(5,0) node[right]{$V (\si{m^3})$};
				\draw[<->] (0,0)--(0,5) node[above]{$P (\si{kPa})$};
				\draw[line width=2pt,blue,-stealth](4,1) -- (2.5,1) node[below]{A} -- (1,1) ;
				\draw[line width=2pt,blue,-stealth](1,1)-- (1,2.5) node [left] {B} -- (1,4);
				\draw[line width=2pt,blue,-stealth] plot[blue,variable=\t,samples=1000,domain=-33:0] ({16*sec(\t)-15},{4.6*(tan(\t))+4});
				\draw [blue](2.5,2.5) node[right] {C};
				\draw (0,1) node[left] {1};
				\draw (0,2) node[left] {2};
				\draw (0,3) node[left] {3};
				\draw (0,4) node[left] {4};
				\draw (0,5) node[left] {5};
				
				\draw (1,0) node[below] {1};
				\draw (2,0) node[below] {2};
				\draw (3,0) node[below] {3};
				\draw (4,0) node[below] {4};
				\draw (5,0) node[below] {5};		
				
				\filldraw [fill=red, draw=black, fill opacity=0.5] (1,0) rectangle (4,1);
			\end{tikzpicture}
		\end{center}	
		Since this shape is a rectangle, we merely multiply base times height:
		
		\begin{equation*}
			W = A = BH = (3 \si{m^3}) (1 \times 10^3 \si{Pa}) = \boxed{3 \times 10^3 \si{J}}
		\end{equation*}
		
		\item Since process B is a vertical segment on the PV-Diagram, there is no area underneath this segment.  Therefore, the are and the work done are both  0 Joules.
		
	\end{enumerate}
	
\end{mdframed}